Online A / B test

### 2016-02-14 3_AB_test/AB_test.Rmd
reorganize doc

1. **Significance Level: ** Denoted by $\alpha$, this threshold governs the chance of false positive. A significance level of 0.05 means that there's a 5 percent chance of false positive.
2. **Statistical power: ** This stands for $1 - \beta$ ( or so called sensitivity ), where $\beta$ represents the probability that you'll get a false negative. So a statistical power of 0.8 means that if there's is in fact a change, there's 80 percent that we'll detect it, which is equivalent to saying that there will be a 20 percent false negative.

>>>>

1. **Significance Level:** Denoted by $\alpha$, this threshold governs the chance of false positive. A significance level of 0.05 means that there's a 5 percent chance of false positive.
2. **Statistical power:** This stands for $1 - \beta$ ( or so called sensitivity ), where $\beta$ represents the probability that you'll get a false negative. So a statistical power of 0.8 means that if there's is in fact a change, there's 80 percent chance that we'll detect it, which is equivalent to saying that there will be a 20 percent false negative.
